Effective Inclusion of Electronic Polarization to a Negatively Charged Membrane

### 2018-12-19 Manuscript/manuscript.tex
Small fixes and moving aroung figures and tables in Methods and Results (beginning)

@@

\begin{table*}[tbp]
\centering
\caption{  List of MD simulations reporting their respective
           added buffer concentrations,
           amounts of individual molecules,
           and the deployed models.
         }\label{tbl:sim-list}
         \todo{SAMULI: All the tails are PO, right? This could be mentioned in the caption.}
\begin{tabular}{l | r r r r | r r | c c }
                          &  \multicolumn{4}{c}{added buffer concentration / mM}    & \multicolumn{2}{c}{no. molecules} &  \multicolumn{2}{c}{simulated with model}  \\
PC:PS (ratio)/counterions &  \ce{K^+}  &  \ce{Na^+} & \ce{Ca^{2+}} & \ce{Cl^-}      & \ce{H2O} &  PC:PS                 &  ECC-lipids  &  Lipid17    \\
  \hline
PC:PS (0:1)/K+   &      0  &      0  &      0  &      0  &  3600  &  0:72  &  X  &  X  \\ 
PC:PS (0:1)/Na+  &      0  &      0  &      0  &      0  &  3600  &  0:72  &  X  &  X  \\ 
  \hline
PC:PS (10:1)/K+  &      0  &      0  &      0  &      0  &  3600  &  60:6  &  X  &  -  \\ 
PC:PS (10:1)/Na+ &      0  &      0  &      0  &      0  &  3600  &  60:6  &  X  &  -  \\ 
  \hline
PC:PS (1:1)/K+   &      0  &      0  &      0  &      0  &  5253  &  64:64  &  X  &  X  \\ 
PC:PS (1:1)/Na+  &      0  &      0  &      0  &      0  &  5253  &  64:64  &  X  &  X  \\ 
  \hline
PC:PS (4:1)/K+   &      0  &      0  &      0  &      0  &  3600  &  48:12  &  X  &  -  \\ 
PC:PS (4:1)/Na+  &      0  &      0  &      0  &      0  &  3600  &  48:12  &  X  &  -  \\ 
  \hline
PC:PS (5:1)/K+   &      0  &      0  &      0  &      0  &  3600  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &      0  &      0  &      0  &      0  &  3600  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &      0  &      0  &     78  &     78  &  3561  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &      0  &      0  &    125  &    125  &  3561  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &      0  &      0  &    202  &    202  &  3561  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &      0  &      0  &    409  &    409  &  3522  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &      0  &      0  &    621  &    621  &  3483  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &      0  &    621  &      0  &    621  &  3483  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &      0  &   1510  &      0  &   1510  &  3377  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &      0  &   3002  &      0  &   3002  &  3213  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &    621  &      0  &      0  &    621  &  3483  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &   1510  &      0  &      0  &   1510  &  3377  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &   3002  &      0  &      0  &   3002  &  3213  &  60:12  &  X  &  X  \\ 
  \hline
\end{tabular}
\end{table*}

\begin{table}[tbp]
  \caption{Simulation parameters}
  \label{tbl:mdpar}
  \begin{tabular}{ll}
    simulation property & parameter   \\
    \hline
    time-step           & 2~fs         \\
    equilibration time  & tba~ns  \\
    total simulation time     & 1.5~$\mu$s  \\
    temperature         & 298~K       \\
    thermostat          & v-rescale  \cite{bussi07}   \\
    barostat            & Parrinello-Rahman, semi-isotropic \cite{parrinello81} \\
    long-range electrostatics & PME  \cite{darden93}  \\
    cut-off scheme      & Verlet \cite{Pall13}      \\
    Coulomb and VdW cut-off & 1.0~nm \\
    constraints         & LINCS, only hydrogen atoms \cite{hess97} \\
    constraints for water & SETTLE  \cite{miyamoto92} \\
    \hline
  \end{tabular}
\end{table}

@@

\begin{figure}[tb!] 
  \centering 
  \includegraphics[width=\figwidth]{../img/ecc_pops/Order-parameters_form-factors_exp-L17-ECC-lipids.pdf}
  \includegraphics[width=\figwidth]{../img/ecc_pops/pops_chemfig.pdf} 
\hfill
  \caption{\label{simVSexpNOions_POPS} 
    Top: X-ray scattering form factors from simulations with the Lipid17 \citep{lipid17-future} and 
    the ECC-POPS models compared with experiments~\citep{kucerka14} at 298~K. 
    Middle: Order parameters of POPS head group, glycerol backbone and acyl chains  
    from simulations with the Lipid17 \citep{lipid17-future} and the ECC-POPS models 
    compared with experiments at 298~K. \citep{nmrlipids_proj4}
    Open/closed symbols are used for palmitoyl/oleoyl chains of POPS. 
    Bottom: The chemical structure of POPS and the labeling of the carbon segments. 
  }  
\end{figure}

\begin{table}[tb!] 
\centering
  \caption{Values of the area per lipid (APL) of POPS bilayers 
	   at 298~K with only \ce{Na^+} counterions and no additional ions. \label{tab:apls} } 
  \begin{tabular}{l|c c} 
%    \multicolumn{3}{c}{POPC} \\
%    model          & APL / Å$^2$   & $T$ / K  \\ 
%    \hline 
%    Lipid14 POPC \citep{melcr18}    & 65.1$\pm$ 0.6  &  300 \\ 
%    Lipid14 POPC \citep{dickson14}  & 65.6$\pm$ 0.5  &  303 \\ 
%    \hline 
%    ECC-POPC     \citep{melcr18}    & 63.2$\pm$ 0.6  &  300       \\ 
%    \hline 
%    experiment (SDP model) \citep{kucerka11} & 64.3  &  303    \\ 
%    \hline 
%    \multicolumn{3}{c}{} \\
%    \multicolumn{3}{c}{POPE} \\
%    model          & APL / Å$^2$   & $T$ / K  \\ 
%    \hline 
%    ECC-POPE                 & 56.7$\pm$ 0.8  &  298 \\ 
%    \hline 
%    experiment   \citep{parsegian89} & 56.6  &  310    \\ 
%    experiment   \citep{rappolt03}   & 59--61 &  303--313  \\ 
%    \hline 
%    \multicolumn{3}{c}{} \\
    \multicolumn{3}{c}{POPS} \\
    model          & APL / Å$^2$   & $T$ / K  \\ 
    \hline 
    Lipid17 POPS              & 53.5$\pm$ 0.8  &  298 \\ 
    \hline 
    ECC-POPS                & 60.3$\pm$ 0.6  &  298       \\ 
    \hline 
    experiment (SDP model) \citep{kucerka14} & 62.3  &  298    \\ 
    \hline 
  \end{tabular} 
\end{table}

\todo{SAMULI: For this discussion we need the counterion density profiles from pure POPS
  simulation with Lipid17 and Dang counterions. This could be added to the figure \ref{fig:POPS-counterions-dens} and
the figure could be moved here.}

@@

@@

\begin{figure}[tbp!] 
  \centering 
  \includegraphics[height=\figheight]{../img/ecc_pops/density_profiles_na-k-counterions_wat_phos_compar_purePOPS_ecclipids-lipid17.pdf}
  \includegraphics[height=\figheight]{../img/ecc_pops/density_profiles_na-k-counterions_wat_phos_compar_5PC-1PS_ecclipids-lipid17.pdf}
  \caption{\label{fig:POPS-counterions-dens}
    Number density profiles of \ce{K^{+}}, \ce{Na^{+}} counterions along the membrane normal axis 
    for the negatively charged bilayers composed of only POPS (left) or POPC:POPS (5:1, right) 
    using ECC-lipids and ECC-ions (solid lines) and Lipid17 (dashed lines).  
    The density profiles of phosphate groups and water are divided by 4 and 100, respectively.  
}
\end{figure}

>>>>

\begin{table*}[tbp]
\centering
\caption{  List of MD simulations reporting their respective
           added buffer concentrations,
           amounts of individual molecules,
           and the deployed models.
           The fatty acid chains for all lipids are plamitoyl (sn-1) and oleoyl (sn-2).
         }\label{tbl:sim-list}
\begin{tabular}{l | r r r r | r r | c c }
                          &  \multicolumn{4}{c}{added buffer concentration / mM}    & \multicolumn{2}{c}{no. molecules} &  \multicolumn{2}{c}{simulated with model}  \\
PC:PS (ratio)/counterions &  \ce{K^+}  &  \ce{Na^+} & \ce{Ca^{2+}} & \ce{Cl^-}      & \ce{H2O} &  PC:PS                 &  ECC-lipids  &  Lipid17    \\
  \hline
PC:PS (0:1)/K+   &      0  &      0  &      0  &      0  &  3600  &  0:72  &  X  &  X  \\ 
PC:PS (0:1)/Na+  &      0  &      0  &      0  &      0  &  3600  &  0:72  &  X  &  X  \\ 
  \hline
PC:PS (10:1)/K+  &      0  &      0  &      0  &      0  &  3600  &  60:6  &  X  &  -  \\ 
PC:PS (10:1)/Na+ &      0  &      0  &      0  &      0  &  3600  &  60:6  &  X  &  -  \\ 
  \hline
PC:PS (1:1)/K+   &      0  &      0  &      0  &      0  &  5253  &  64:64  &  X  &  X  \\ 
PC:PS (1:1)/Na+  &      0  &      0  &      0  &      0  &  5253  &  64:64  &  X  &  X  \\ 
  \hline
PC:PS (4:1)/K+   &      0  &      0  &      0  &      0  &  3600  &  48:12  &  X  &  -  \\ 
PC:PS (4:1)/Na+  &      0  &      0  &      0  &      0  &  3600  &  48:12  &  X  &  -  \\ 
  \hline
PC:PS (5:1)/K+   &      0  &      0  &      0  &      0  &  3600  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &      0  &      0  &      0  &      0  &  3600  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &      0  &      0  &     78  &     78  &  3561  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &      0  &      0  &    125  &    125  &  3561  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &      0  &      0  &    202  &    202  &  3561  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &      0  &      0  &    409  &    409  &  3522  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &      0  &      0  &    621  &    621  &  3483  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &      0  &    621  &      0  &    621  &  3483  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &      0  &   1510  &      0  &   1510  &  3377  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &      0  &   3002  &      0  &   3002  &  3213  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &    621  &      0  &      0  &    621  &  3483  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &   1510  &      0  &      0  &   1510  &  3377  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &   3002  &      0  &      0  &   3002  &  3213  &  60:12  &  X  &  X  \\ 
  \hline
\end{tabular}
\end{table*}

@@

\begin{table}[tbp]
  \caption{Simulation parameters}
  \label{tbl:mdpar}
  \begin{tabular}{ll}
    simulation property & parameter   \\
    \hline
    time-step           & 2~fs         \\
    equilibration time  & 50~ns  \\
    total simulation time     & 1~$\mu$s  \\
    temperature         & 298~K       \\
    thermostat          & v-rescale  \cite{bussi07}   \\
    barostat            & Parrinello-Rahman, semi-isotropic \cite{parrinello81} \\
    long-range electrostatics & PME  \cite{darden93}  \\
    cut-off scheme      & Verlet \cite{Pall13}      \\
    Coulomb and VdW cut-off & 1.0~nm \\
    constraints         & LINCS, only hydrogen atoms \cite{hess97} \\
    constraints for water & SETTLE  \cite{miyamoto92} \\
    \hline
  \end{tabular}
\end{table}

@@

\begin{figure}[tb!] 
  \centering 
  \includegraphics[width=\figwidth]{../img/ecc_pops/Order-parameters_form-factors_exp-L17-ECC-lipids.pdf}
  \includegraphics[width=\figwidth]{../img/ecc_pops/pops_chemfig.pdf} 
\hfill
  \caption{\label{simVSexpNOions_POPS} 
    \textbf{Top:} X-ray scattering form factors from simulations with Lipid17/Dang \citep{lipid17-future, dang2006} and 
    the ECC-POPS/ECC-ions \cite{martinek17, Pluhackova2016} compared with experiments~\citep{kucerka14} at 298~K. 
    \textbf{Middle:} Order parameters of POPS head group, glycerol backbone and acyl chains  
    from simulations with the Lipid17 \citep{lipid17-future} and the ECC-POPS models 
    compared with experiments at 298~K. \citep{nmrlipids_proj4}
    Open/closed symbols are used for palmitoyl/oleoyl chains of POPS. 
    \textbf{Bottom:} The chemical structure of POPS and the labeling of the carbon segments. 
  }  
\todo{J: flip the chemical structure so that it agrees with the left-to-right reading of the plot.}
\end{figure}

\begin{table}[tb!] 
\centering
  \caption{Values of the area per lipid (APL) of POPS bilayers 
	   at 298~K with only \ce{Na^+} counterions and no additional ions. \label{tab:apls} } 
  \begin{tabular}{l|c } 
    \multicolumn{2}{c}{POPS} \\
    model          & APL / Å$^2$    \\ 
    \hline 
    Lipid17/Dang              & 53.5$\pm$ 0.8   \\ 
    Lipid17/ff99 \todoi{add?} & XX.x$\pm$ 0.8   \\ 
    \hline 
    ECC-POPS/ECC-ions         & 60.3$\pm$ 0.6   \\ 
    \hline 
    experiment (SDP model) \citep{kucerka14} & 62.3  \\ 
    \hline 
  \end{tabular} 
\end{table}

@@

\begin{figure}[tbp!] 
  \centering 
  \includegraphics[height=\figheight]{../img/ecc_pops/density_profiles_na-k-counterions_wat_phos_compar_purePOPS_ecclipids-lipid17.pdf}
  \includegraphics[height=\figheight]{../img/ecc_pops/density_profiles_na-k-counterions_wat_phos_compar_5PC-1PS_ecclipids-lipid17.pdf}
  \caption{\label{fig:POPS-counterions-dens}
    Number density profiles of \ce{K^{+}}, \ce{Na^{+}} counterions along the membrane normal axis 
    for the negatively charged bilayers composed of only POPS (left) or POPC:POPS (5:1, right) 
    using ECC-lipids/ECC-ions (solid lines) and Lipid17/Dang ions (dashed lines).  
    The density profiles of phosphate groups and water are divided by 4 and 100, respectively.  
}
\end{figure}

@@
